Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
typos

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.  Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sampling and holding
processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by a ADC and the digital input provided by ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use only the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

@@

\begin{myassumption}
%
\label{assumption:cont_and_plant}
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded. Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  may be considered a sufficient discrete-time representation of $G(s)$.
%
\end{myassumption}

Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}

>>>>

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.  Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sample and hold
processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

@@

\begin{myassumption}
%
\label{assumption:cont_and_plant}
The controller and the plant are linear time-invariant (LTI) systems, {\it i.e.}, any source of
nonlinearity ({\it e.g.}, saturation, overflow, ADC/DAC nonlinearities) will
be disregarded. Additionally, the pulse transfer function obtained via \eqref{eq:pulsetf} using an appropriate sample rate ({\it i.e.}, obeying the Nyquist sampling conditions)  is a precise discrete-time representation of $G(s)$.
%
\end{myassumption}

Although the pulse transfer function $G(z)$ represents adequately $G(s)$ in the z-domain, the model $G(z)$ may not be accurate and some uncertainties may not be covered by that model. These uncertainties may be parametrically expressed by an additive transfer function $\Delta G(z)$, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=G(z)+\Delta G(z),
\end{equation}
that may be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}.
\end{equation}
